ICM testing

### 2023-11-29 Scripts/Paper_1.Rmd
Mostly new figures
Mostly focused on building better figures for the paper, some other general tweaks.

```{r paper-other-metrics}

# We are now looking at everything, lifetime reproductive success

for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")

# 
# cod <- grep("morhua",names(for.tune.summary))
# haddock <- grep('aeglefinus',names(for.tune.summary))
# herring <- grep("harengus",names(for.tune.summary))
# pollock <- grep("virens",names(for.tune.summary)) 
# sole <- grep("solea",names(for.tune.summary))
# euro.plaice <- grep("platessa",names(for.tune.summary))
# am.plaice <- grep("platessoides",names(for.tune.summary))
# 
# p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))

Stocks <- names(for.tune.summary)
n.stocks <- length(Stocks)

for.tune.stocks <- NULL
for(i in 1:n.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]
  tmp <- for.tune.summary[[nam]]
  tmp$Management   <- meta$Management  
  tmp$Area <- meta$Area
  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") tmp$Area <- "GB (West)"
  tmp$Order <- meta$Order
  tmp$Family   <- meta$Family  
  tmp$Genus  <- meta$Genus 
  tmp$Species <- meta$Species
  tmp$Model <- meta$Model
  tmp$Meeting_or_reference <- meta$Meeting_or_reference
  tmp$Notes <- meta$Notes
  #tmp$removals.init <- rem.tmp[[nam]]$rem
  for.tune.stocks[[nam]] <- tmp
}

# Now unpack them...
for.tunes <- do.call("rbind",for.tune.stocks)
# Typo clean up...
for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
for.tunes$Species[for.tunes$Species=="Aeglefinus"] <- "aeglefinus"
for.tunes$Species[for.tunes$Species=="Solea"] <- "solea"

# What Stocks suck
# sucker.check <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
#                                                                           max = max(per.diff,na.rm=T))
# View(sucker.check)
# 
# # FM issues are all really related to having very low fishing mortality years...
# # Not really sure how to handle that... maybe an if in the code to make a big jump if model is nowhere on convergence
# # and fishing is < 10% of mean F for the population, that would cover all the problems I'm seeing here.
# # Has years with 0 fishing, need to put in something
# "ICES-WGNSSK_NS4 _Scopthalmus_maximus"
# "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"
# # Removals so low the step size isn't enough...
# "DFO_3Pn-4RS_Gadus_morhua" # Worked great until the second last year then it did nothing, I think the step size was too small
# "DFO_4T-4VN_Gadus_morhua" # In 1995 it just does nothing, I think because the step size is too small due to super low F.
# "DFO_4T_Hippoglossoides _platessoides"
# "NEFSC-GARMIII_GOM-CHATT_Morone_saxatilis"
# tst <- for.tunes %>% dplyr::filter(Stock == "ICES-HAWG_NS_Ammodytes_dubius")
# 
# # Now what does this look like...
# paper.stocks <- unique(for.tunes$Stock)
# 
# tst <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
#                                                                  max = max(per.diff, na.rm=T))
# # Now the doubling time simulations for each stock

dt.res <- NULL
for(i in paper.stocks)
{
  try <- for.tunes %>% dplyr::filter(Stock == i)
  double.time <- NA
  pop <- 1000

for(s in 1:100)
{
for(y in 2:100)
{
  lambda <- sample(na.omit(try$lambda),size=1)
  pop[y] <- lambda*pop[y-1]
} # end the years loop
tmp <- which(pop >= 2*pop[1])[1]

if(is.na(tmp)) double.time[s] <- 0
if(!is.na(tmp))double.time[s] <- tmp
} # end sim loop

dt.res[[i]] <- data.frame(dt = double.time,Stock = i,Species = try$Species[1])

@@

# Now to get generation lengths + reproductive rates....
# First I need to get the fecundity and natural mortalities by cohort instead of year.

res.fin <- NULL
res.year.fin <- NULL
for(i in paper.stocks)
{
  tst <- for.tune.all[[i]]
  # Fishing mortality
  fm.org.tmp <- fs.tmp[[i]]
  fm.tmp <- tst$fm.opt
  # fecundity
  fec.tmp <- tst$fecund.opt
  fec.org.tmp <- tst$fecund.org
  # Natural mortality
  m.org.tmp <- exp(-tst$nm.org)
  m.tmp <- exp(-tst$nm.opt)
  # Total mortality
  z.tmp <- exp(-tst$z.opt)
  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp)

  ages <- 0:(ncol(fec.tmp)-1)
  n.ages <- length(ages)
  years <- tst$res$year
  n.years <- length(years)
  # Now I need to grab the fecundities and nat morts by cohort
  if(n.years > n.ages)
  {
  res.cohort <- NULL
  res.year <- NULL
  for(y in 1:(n.years-n.ages+1))
  {
    count = 0
    fs <- NA
    lx <- 1
    fs.org <- NA
    lx.org <- 1
    lx.year <- 1
    for(a in 1:n.ages)
    {
    fs[a] <- fec.tmp[y+count,a]  
    fs.org[a] <- fec.org.tmp[y+count,a]  
    if(a > 1) 
    {
      lx[a] <- lx[a-1] * m.tmp[y+count,a]  
      lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
      lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
    }  # end the a > 1 if
    count <- count + 1
    }# end the ages loop
    res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
                           mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                           x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                           cohort=years[y],Stock = i)

    res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
                           mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
                           x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                           year=years[y],Stock = i)

@@

# unpack it...
res.fin[[i]] <- do.call('rbind',res.cohort)
res.year.fin[[i]] <- do.call('rbind',res.year)
}  # end if to make sure we have enough data to get the cohort estimates.

}# end the stock loop
res.cohort.final <- do.call('rbind',res.fin)
res.year.final <- do.call('rbind',res.year.fin)

pop.dam <- res.cohort.final %>% dplyr::group_by(cohort,Stock) %>% dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
                                                                R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
pop.dam <- data.frame(pop.dam,Management=NA,Area = NA,Order=NA,
                      Family=NA,Genus=NA,Species=NA,Model=NA,Meeting_or_reference = NA,Notes = NA)

for(i in 1:n.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]

  pop.dam$Management[pop.dam$Stock == nam]   <- meta$Management  
  pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") pop.dam$Area[pop.dam$Stock == nam] <- "GB (West)"
  pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
  pop.dam$Family[pop.dam$Stock == nam]   <- meta$Family  
  pop.dam$Genus[pop.dam$Stock == nam]  <- meta$Genus 
  pop.dam$Species[pop.dam$Stock == nam] <- meta$Species
  pop.dam$Model[pop.dam$Stock == nam] <- meta$Model
  pop.dam$Meeting_or_reference[pop.dam$Stock == nam] <- meta$Meeting_or_reference
  pop.dam$Notes[pop.dam$Stock == nam] <- meta$Notes

pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"
pop.dam$Species[pop.dam$Species=="Aeglefinus"] <- "aeglefinus"
pop.dam$Species[pop.dam$Species=="Solea"] <- "solea"

@@

```{r simp-figs}

ggplot(for.tunes) + geom_jitter(aes(y=lambda,x=Species,group=Stock,color=Stock)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10))

ggplot(for.tunes) + geom_jitter(aes(y=lambda.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (lambda)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))

unique(for.tunes$Species)
windows(11,11)
ggplot(dub.time) + geom_jitter(aes(y=dt,x=Species),alpha=0.05,fill="black",color="black",shape=22) + 
                   scale_y_continuous(name = 'Doubling time (years)',breaks = seq(0,100,by=5))

ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))

windows(11,11)
ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + ylab("Generation Length (years)")

#options(scipen=999)
r0.plt <- ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
                            scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.05,0.1,0.5,1,5,10,50,100),minor_breaks = NULL) + 
                            facet_wrap(~Species,scales = 'free')+
                            theme(axis.text.x = element_text(angle =45,hjust=1))
save_plot("D:/Github/ICM/Figures/tuned/R0_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

windows(11,11)
r0.ts.plt <- ggplot(pop.dam) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area))  + 
                            scale_y_log10(name = "Lifetime Reproductive Output")+#, breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
                            facet_wrap(~Species,scales = 'free')+
                            theme(axis.text.x = element_text(angle =45,hjust=1))
r0.ts.plt
save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

vickis.cols <- sort(rep(c( "#172582",  "#F8DC91", "#FBB891", "#FB6A01", "#B80000"),3))
linetypes <- rep(c(1,2,4),5)

windows(11,11)
cod.r0.ts.plt <- ggplot(pop.dam %>% dplyr::filter(Species == 'morhua')) + geom_line(aes(y=R0.opt,x=cohort,group=Area,color=Area,linetype=Area),size=1.5)  + 
                            scale_y_log10(name = "Lifetime Reproductive Output", breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) + 
                            scale_color_manual(values = vickis.cols) +
                            scale_linetype_manual(values = linetypes) +
                            theme(legend.key.width  = unit(2, "cm"))
cod.r0.ts.plt
#save_plot("D:/Github/ICM/Figures/tuned/R0_timeseries_ignoring_fishing.png",r0.plt,base_width = 8,base_height = 8)

windows(11,11)
ggplot(pop.dam %>% dplyr::filter(Species =="morhua")) + geom_boxplot(aes(y=R0.opt,x=Area))  + 
                                                        scale_y_log10(name = "Lifetime Reproductive Output",breaks = c(0.001,0.01,0.1,1,5,10,50,100),minor_breaks = NULL) +
                                                        theme(axis.text.x = element_text(angle =45,hjust=1))

# Missing catch questions
# first did we do much to the Fecundity term to get here
quantile(for.tunes$mean.fec/for.tunes$mean.vpa.fec,probs=seq(0.01,1,0.01),na.rm=T)

>>>>

```{r paper-other-metrics-and-metadata}

# We are now looking at everything, lifetime reproductive success
model <- "fec_nm"
for.tune.summary <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_summary_",model,".Rds"))
for.tune.all <- readRDS(paste0("D:/Github/ICM/Results/forwards_fully_tuned_all_res_",model,".Rds"))

load(file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))
# Get the stocks...
Stocks <- names(for.tune.summary)
n.stocks <- length(Stocks)

############ Meta data and clean up, could be it's own chunk really, but it's really fast, so meh...

#  A quick way to get the other potentially interesting info for the stock...
drop <- which(names(ASR_long) %in% c("Year","type","age","value"))
meta <- NULL
for(i in Stocks) meta[[i]] <- ASR_long[ASR_long$Stock == i,-drop][1,]
meta <- do.call('rbind',meta)

# First making a meta data object and adding a bunch of columns to it... very messy!!
meta$Species[meta$Species == ' harengus']  <- "harengus"
meta$Species[meta$Species == "Aeglefinus"] <- "aeglefinus"
meta$Species[meta$Species == "Solea"] <- "solea"
meta$Genus[meta$Genus == " Hippoglossoides"] <- "Hippoglossoides"
meta$G.short <- toupper(paste0(substr(meta$Genus,1,1),"."))
meta$G.Species <- paste0(meta$G.short," ",meta$Species)
# Simplified Management
meta$Manage.short <- meta$Management
meta$Manage.short[grep("TRAC",meta$Management)] <- "DFO-TRAC"
meta$Manage.short[grep("DFO",meta$Management)] <- "DFO-TRAC"
meta$Manage.short[grep("NEFSC",meta$Management)] <- "NEFSC"
meta$Manage.short[grep("ICES",meta$Management)] <- "ICES"

# The 3 pieces of the ocean
meta$LME <- "NW Atlantic"
meta$LME[meta$Management == "AFSC"] <- "Pacific (Alaska)"
meta$LME[grepl("ICES",meta$Management)] <- "NE Atlantic"
# Some other Area summaries
meta$Area.broad <- meta$Area
meta$Area.long <- meta$Area
meta$Area.narrow <- "" # Leave this blank if not needed

meta$Area.broad[grep("NS",meta$Area)] <- "NS"
meta$Area.long[grep("NS",meta$Area)] <- "North Sea"
meta$Area.broad[grep("CS",meta$Area)] <- "CS"
meta$Area.long[grep("CS",meta$Area)] <- "Celtic Sea"
meta$Area.broad[grep("ROCK6b",meta$Area)] <- "CS"
meta$Area.long[grep("ROCK6b",meta$Area)] <- "Celtic Sea Rockall"
meta$Area.broad[grep("IS",meta$Area)] <- "IS"
meta$Area.long[grep("IS",meta$Area)] <- "Irish Sea"
meta$Area.broad[grep("BS",meta$Area)] <- "BS"
meta$Area.long[grep("BS",meta$Area)] <- "Baltic Sea"
meta$Area.broad[grep("NEA",meta$Area)] <- "NEA"
meta$Area.long[grep("NEA",meta$Area)] <- "NE Arctic"
meta$Area.broad[grep("B28.1",meta$Area)] <- "BS"
meta$Area.long[grep("B28.1",meta$Area)] <- "Baltic Sea"
meta$Area.broad[grep("SP8abd",meta$Area)] <- "BoB"
meta$Area.long[grep("SP8abd",meta$Area)] <- "Bay of Biscay"
meta$Area.broad[grep("FA",meta$Area)] <- "I-F"
meta$Area.broad[grep("ICE",meta$Area)] <- "I-F"
meta$Area.long[grep("FA",meta$Area)] <- "Faroes"
meta$Area.long[grep("ICE",meta$Area)] <- "Iceland"

meta$Area.broad[grep("GOM",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("GOM",meta$Area)] <- "Gulf of Maine"
meta$Area.broad[grep("GB",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("GB",meta$Area)] <- "Georges Bank"
meta$Area.broad[grep("5Y",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("5Y",meta$Area)] <- "NAFO 5Y"
meta$Area.broad[grep("5Z",meta$Area)] <- "GOM-GB"
meta$Area.long[grep("5Z",meta$Area)] <- "NAFO 5Z"
meta$Area.broad[grep("USATL",meta$Area)] <- "GOM-GB" # The fishery is broader than just GOM, but it does also include it.
meta$Area.long[grep("USATL",meta$Area)] <- "US Atlantic" # The fishery is broader than just GOM, but it does also include it.
meta$Area.broad[grep("NWA",meta$Area)] <- "GOM-GB" # Mackerel... so that definition is a bit narrow....
meta$Area.long[grep("NWA",meta$Area)] <- "US Atlantic" # Mackerel... so that definition is a bit narrow....
#meta$Area1[grep("SNE- MA",meta$Area)] <- "GOM-GB" # YT in US, so no GB so that definition is a bit narrow....
meta$Area.broad[grep("MA",meta$Area)] <- "GOM-GB" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
meta$Area.long[grep("MA",meta$Area)] <- "Gulf of Maine" # YT  and summer flounder in US, so no GB so that definition is a bit narrow....
meta$Area.broad[grep("BSAI",meta$Area)] <- "BSAI"
meta$Area.broad[grep("4T",meta$Area)] <- "GSL"
meta$Area.long[grep("4T",meta$Area)] <- "NAFO 4T"
meta$Area.broad[grep("2J3",meta$Area)] <- "NFLD"
meta$Area.long[grep("2J3",meta$Area)] <- "NFLD"
meta$Area.broad[grep("3Pn-4RS",meta$Area)] <- "NFLD"
meta$Area.long[grep("3Pn-4RS",meta$Area)] <- "NFLD"
meta$Area.long[grep("GOA",meta$Area)] <- "Gulf of Alaska"
meta$Area.long[grep("AI",meta$Area)] <- "Aleutian Islands"
meta$Area.long[grep("ESB",meta$Area)] <- "Bering Sea"
meta$Area.long[grep("BSAI",meta$Area)] <- "Bering Sea & AI"
meta$Area[grep("BASI-Females",meta$Area)] <- "BSAI-Females"
meta$Area.long[grep("BSAI-Females",meta$Area)] <- "Bering Sea & AI"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Pollachius_virens"] <- "5b"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5a_Pollachius_virens"] <- "5a"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS4 _Solea_solea"] <- "4"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d._Solea_solea"] <- "7d"
meta$Area.narrow[meta$Stock == "ICES-WGBFAS_NS IIIa 22-24_Solea_Solea"] <- "22-24"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 7d_Pleuronectes_platessa"] <- "7d"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4,20_Pleuronectes_platessa"] <- "4 20"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS7e_Pleuronectes_platessa"] <- "7e"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_IS27.7a_Pleuronectes_platessa"] <- "7a"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FA5b_Melanogrammus_aeglefinus"] <- "5b"
meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Melanogrammus_aeglefinus"] <- "5a"
meta$Area.narrow[meta$Stock == "ICES-WGBFAS_B28.1_Clupea_harengus"] <- "28"
meta$Area.narrow[meta$Stock == "ICES-WGBFAS_BS 25-29-32_Clupea_harengus" ] <- "25-32"
meta$Area.narrow[meta$Stock == "ICES-HAWG_WBS 22-24_Clupea_harengus"] <- "22-24"
meta$Area.narrow[meta$Stock == "DFO_4T-Fall_Clupea_harengus"] <- "Fall"
meta$Area.narrow[meta$Stock == "DFO_4T-Spring_Clupea_harengus"] <- "Spring"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS27.6a_Merlangius_merlangus"] <- "27.6a"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_CS7a_Merlangius_merlangus"] <- "7a"
meta$Area.narrow[meta$Stock == "ICES-NWWG_ICE5a_Gadus_morhua"] <- "5a"
meta$Area.narrow[meta$Stock == "ICES-NWWG_FAPL5b1_Gadus_morhua" ] <- "5b"
meta$Area.narrow[meta$Stock == "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua"] <- "4-7 20"
meta$Area.narrow[meta$Stock == "ICES-WGCSE_NS6a_Gadus_morhua"] <- "6a"
meta$Area.narrow[meta$Stock == "DFO_2J3KL_Gadus_morhua"] <- "2J 3KL"
meta$Area.narrow[meta$Stock == "DFO_3Pn-4RS_Gadus_morhua"] <- "3Pn 4RS"
meta$Area.narrow[meta$Stock == "NEFSC-CERT-TRAC_GB _Gadus_morhua"] <- "East"

meta$Stock.short <- paste0(meta$Area.long," ",meta$Area.narrow," ",meta$G.short," ",meta$Species)
meta$Stock.no.species <- paste0(meta$Area.long," ",meta$Area.narrow)

for.tune.stocks <- NULL
fta <- NULL

# Going to rename these female stocks.
fem.names <- c("AFSC_BASI-Females_Pleuronectes_quadrituberculatus",
                  "AFSC_EEBSAI-Females_Lepidopsetta_polyxystra",
                  "AFSC_BSAI-females_Atheresthes_stomais")
fem.rename <- c("AFSC_BSAI_Pleuronectes_quadrituberculatus",
                  "AFSC_EEBSAI_Lepidopsetta_polyxystra",
                  "AFSC_BSAI_Atheresthes_stomais")
# Going to drop these stocks
dont <- paste(c("Mles","Males","COASTNOR"),collapse = "|")

meta.sub <- NULL
for(i in Stocks) 
{
  org.nam <- i
  tmp <- for.tune.summary[[org.nam]]
  new.stock.nam <- org.nam
  # Don't bother for these stocks...
  if(!grepl(dont,tmp$Stock[1]))
  {
    # Grab the metadata and add in some new useful things...
    meta.sub[[i]] <- meta[meta$Stock == org.nam,]

    # Rename the ladies
    if(tmp$Stock[1] == fem.names[1]) new.stock.nam <- tmp$Stock <- fem.rename[1]
    if(tmp$Stock[1] == fem.names[2]) new.stock.nam <- tmp$Stock <- fem.rename[2]
    if(tmp$Stock[1] == fem.names[3]) new.stock.nam <- tmp$Stock <- fem.rename[3]

    meta.sub[[i]]$Stock <- new.stock.nam
    tmp <- data.frame(tmp,meta.sub[[i]])
    # For tunes all
    fta[[new.stock.nam]] <- for.tune.all[[org.nam]]
    fta[[new.stock.nam]]$meta <- meta.sub[[i]]
    for.tune.stocks[[new.stock.nam]] <- tmp
  }# End skip stocks...
}
# Now unpack them...
for.tunes <- do.call("rbind",for.tune.stocks)
for.tune.all <- fta
meta.sub <- do.call("rbind",meta.sub)

######################### End Meta data and clean up #####################

# Now some summaries...

# Reset on the stocks...
Stocks <- sort(names(for.tune.all))
n.stocks <- length(Stocks)

# Doubling time, no fishing
dt.res <- NULL
n.dt.sims <- 20 # Number of simultions...
n.years <- 100
for(i in Stocks)
{
  try <- for.tunes %>% dplyr::filter(Stock == i)
  meta.tmp <- meta.sub %>% dplyr::filter(Stock == i)
  double.time <- NA
  pop <- 1000
  tmp.res <- NULL
for(s in 1:n.dt.sims)
{
  tmp <- rep(0,n.years)

  for(y in 2:n.years)
  {
    lambda <- sample(na.omit(try$lambda),size=1)
    pop[y] <- lambda*pop[y-1]
    if(pop[y] >= 2*pop[1] & tmp[y] == 0) tmp[y:n.years] <- 1
  } # end the years loop
  tmp.res[[s]] <- data.frame(year =1:100,doubled = tmp,sim=s)
  } # end sim loop
  res.tmp <- do.call("rbind",tmp.res)

dt.res[[i]] <- data.frame(res.tmp,meta.tmp)

@@

dub.time.summary <- dub.time %>% dplyr::group_by(Stock,year)  %>% dplyr::summarise(prop = sum(doubled)/n.dt.sims)
dub.time.summary <- left_join(dub.time.summary,meta.sub,by="Stock")

# Now to get generation lengths + reproductive rates....
# First I need to get the fecundity and natural mortalities by cohort instead of year.
res.fin <- NULL
res.year.fin <- NULL
res.lambda.fin <- NULL
for(i in Stocks)
{
  tst <- for.tune.all[[i]]
  meta.tmp <- tst$meta
  # Fishing mortality
  fm.org.tmp <- tst$fm.org
  fm.tmp <- tst$fm.opt
  # fecundity
  fec.tmp <- tst$fecund.opt
  fec.org.tmp <- tst$fecund.org
  # Natural mortality
  m.org.tmp <- exp(-tst$nm.org) # This is survivorship
  m.tmp <- exp(-tst$nm.opt) # This is survivorship
  # Total mortality
  z.tmp <- exp(-tst$z.opt) # This is survivorship
  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp) # This is survivorship

  ages <- 0:(ncol(fec.tmp)-1)
  n.ages <- length(ages)
  years <- tst$res$year
  n.years <- length(years)
  # Now I need to grab the fecundities and nat morts by cohort
  if(n.years > n.ages)
  {
  res.cohort <- NULL
  res.year <- NULL
  res.lambda <- NULL
  for(y in 1:(n.years-n.ages+1))
  {
    count = 0
    fs <- NA
    lx <- 1
    fs.org <- NA
    lx.org <- 1
    lx.year <- 1
    for(a in 1:n.ages)
    {
    fs[a] <- fec.tmp[y+count,a]  
    fs.org[a] <- fec.org.tmp[y+count,a]  
    if(a > 1) 
    {
      lx[a] <- lx[a-1] * m.tmp[y+count,a]  
      lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
      lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
    }  # end the a > 1 if
        count <- count + 1
    }# end the ages loop
        res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
                               mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                               x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                               cohort=years[y],meta.tmp)

        res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
                               mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
                               x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                               year=years[y],meta.tmp)

@@

# Do a years loop to get lambda with no fishing for each year, rather than by cohort...
  for(yy in 1:n.years)
  {
    nm <- as.numeric(tst$nm.opt[yy,])
    z <- as.numeric(tst$z.opt[yy,])
    fec <- as.numeric(tst$fecund.opt[yy,])
    nm.init <- as.numeric(tst$nm.org[yy,])
    fec.init <- as.numeric(tst$fecund.org[yy,])
    z.init <- as.numeric(tst$z.org[yy,])
    lam.no.fish <- exp(simple.lotka.r(Z = nm,fecund = fec,ages=ages)$res)
    lam.fish <- exp(simple.lotka.r(Z = z,fecund = fec,ages=ages)$res)
    lam.org.no.fish <- exp(simple.lotka.r(Z = nm.init,fecund = fec.init,ages=ages)$res)
    lam.org.fish <- exp(simple.lotka.r(Z =  z.init,fecund = fec.init,ages=ages)$res)

    # Now summarize these
    res.lambda[[yy]] <-  data.frame(lam.no.fish = lam.no.fish,lam.fish = lam.fish,
                                    lam.org.no.fish = lam.org.no.fish,
                                    lam.org.fish = lam.org.fish,
                                    year=years[yy],meta.tmp)
  } # End the yy loop to get the lambdas...
# unpack it...
res.fin[[i]] <- do.call('rbind',res.cohort)
res.year.fin[[i]] <- do.call('rbind',res.year)
res.lambda.fin[[i]] <-  do.call('rbind',res.lambda)
}  # end if to make sure we have enough data to get the cohort estimates.

}# end the stock loop

res.cohort.final <- do.call('rbind',res.fin)
res.year.final <- do.call('rbind',res.year.fin)
res.lambda.final <- do.call('rbind',res.lambda.fin)

pop.dam <- res.cohort.final %>% dplyr::group_by(cohort,Stock) %>% dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
                                                                R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
pop.dam <- left_join(pop.dam,meta.sub,by="Stock")

dub.time.summary <- data.frame(dub.time.summary)
pop.dam <- data.frame(pop.dam)
# saveRDS(pop.dam,paste0("D:/Github/ICM/Results/R0_and_gen_length_",model,".Rds"))
# saveRDS(dub.time.summary,paste0("D:/Github/ICM/Results/doubling_time_",model,".Rds"))
# saveRDS(for.tunes,paste0("D:/Github/ICM/Results/forward_tunes_for_figures_",model,".Rds"))
save(dub.time.summary,pop.dam,res.year.final,res.cohort.final,for.tunes,dub.time,for.tune.all,res.lambda.final,meta,meta.sub,
     file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))

write.csv(meta.sub, "D:/Github/ICM/Data/metadata.csv")

@@

```{r simp-figs}
theme_set(theme_few(base_size = 14))
model <- 'fec_nm'
load(file=paste0("D:/Github/ICM/Results/all_cleaned_forward_tune_summaries_",model,".Rdata"))

pop.dam.6 <- pop.dam %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
for.tunes.6 <- for.tunes %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
res.lambda.final.6 <- res.lambda.final %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
dub.time.6 <- dub.time.summary %>% dplyr::filter(Species %in% c('morhua','harengus','aeglefinus','virens','solea','platessa'))
# Lambda plot

res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(LME,Area.broad) %>%
                                             dplyr::mutate(Stock.no.species = forcats::fct_inorder(factor(Stock.no.species, ordered=TRUE)))

res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::arrange(Species,Area.broad) %>%
                                             dplyr::mutate(Stock.short = forcats::fct_inorder(factor(Stock.short, ordered=TRUE)))

res.lambda.final.6 <- res.lambda.final.6 %>% dplyr::group_by(Stock) %>% 
                                            dplyr::mutate(lam.no.fish.mn = mean(lam.no.fish,na.rm=T),
                                                          lam.fish.mn = mean(lam.fish,na.rm=T),
                                                          lam.org.no.fish.mn = mean(lam.org.no.fish,na.rm=T),
                                                          lam.org.fish.mn = mean(lam.org.fish,na.rm=T))

#hmm <- merge(tst,res.lambda.final.6,by="Stock")

# So this is lambda with fishing included
lambda.plt <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.no.fish,x=Stock.no.species))  + 
                                           geom_point(aes(y=lam.no.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
                                           geom_hline(yintercept = 1,linetype='dashed') +
                                           facet_wrap(~G.Species,scales='free')+
                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))

save_plot("D:/Github/ICM/Figures/tuned/lambda_no_fishing_6.png",lambda.plt,base_width = 12,base_height = 10)

# With fishing
lambda.plt.fish <- ggplot(res.lambda.final.6) + geom_boxplot(aes(y=lam.fish,x=Stock.no.species))  + 
                                           geom_point(aes(y=lam.fish.mn,x=Stock.no.species),color='blue',shape=8,fill='blue') +
                                           xlab("") + scale_y_log10("lambda",breaks = c(0.4,0.6,0.8,1,1.25,1.75,3,5,10)) + 
                                           geom_hline(yintercept = 1,linetype='dashed') +
                                           facet_wrap(~G.Species,scales='free')+
                                           theme(axis.text.x = element_text(angle =45,hjust=1),legend.position = 'none',
                                                 plot.margin = margin(0,0.5,0,0.5, "cm"),axis.title.y = element_text(margin = margin(r = 30)))

save_plot("D:/Github/ICM/Figures/tuned/lambda_with_fishing_6.png",lambda.plt.fish,base_width = 12,base_height = 10)

# Time series of lambdas....
col.try <- rep(rep(c("black","blue","orange",'firebrick2','lightgreen'),3),20)
#col.try <- rep(c(rep("black",3),rep("blue",3),rep('orange',3),rep('firebrick2',3),rep('lightgreen',3)),20)
pty <- rep(c(rep(21,5),rep(22,5),rep(23,5)),20)
#pty <- rep(rep(c(21:23),5),20)
